Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-06-30 paper.tex
[add] initial text on DoS

>>>>

%-------------------------------------------------------------------------- sec
\section{\uppercase{Denial of Service}}
\label{sec:dos}
\mEdhoc{} includes no specific measures for countering Denial of Service (DoS)
attacks and delegates the responsibility to handle this to the application.
%
\mEdhoc{} itself has limited functionality, few negotiable parameters and
processing rules
%
Hence, we argue in this section that the attack surface
is small from a DoS perspective.
%
However, \mEdhoc{} leaves much of the semantics of its messages undefined.
%
This increases the risk of applications vulnerable to DoS even if \mEdhoc{} is
arguably not vulnerable to DoS itself.
%

Section 8.7 of the \mEdhoc{} specification explains the design philosophy w.r.t.
DoS in two paragraphs and gives two recommendations.
%
The first being that mitigation of DoS based on sending proper messages should
be handled by lower layers, e.g., by checking reachability of the sending
party\footnote{Karl: this may be another way to perform reflection DoS attacks}.
%
The second being that an application may try to determine (in some way) that an
apparently valid message is in fact probably a forgery and should be ignored or
cause processing to stop.
%
